The Astropy Project

### 2017-11-21 main.tex
More minor wording

\subsection{Support of Astropy}

The \astropy project, as of the v2.0 release, does not receive any direct financial support for
the development of the \astropypkg.  Development of the \astropypkg is supported
by individuals who work on \astropy project in their own personal
time, by individuals or groups to work on \astropy as 
part of a research project, or contributions from institutes that allocate 
people to work on \astropy. 
A list of organizations that have contributed to \astropy
are listed in the Acknowledgements.  
Different models have been proposed for support of \astropy in the future 
(ie. \cite{2016arXiv161003159M}), but a long-term plan
for sustainability has not yet been established.
The \astropy project has the ability to accept financial contributions 
(individual or institutes) through the NumFOCUS organization\footnote{NumFOCUS 
is a 501(c)(3) nonprofit that supports and promotes world-class, innovative, 
open source scientific computing.},  
which generally covers the direct costs incurred by the \astropy project.

% Removing unless this gets written about in
% a later version
% This section should be a straight forward/factual description of the current
% funding and support provided to astropy with the purpose of explaining the
% current structure to the community

@@

\section{Astropy Core Package v2.0}
\label{sec:core}
% Adrian
The \astropy project aims to provide \python-based packages for all tasks that
are commonly needed in a large subset of the astronomical community.
At the foundation is the \astropypkg core package, which provides general
functionality (e.g., coordinate transformations, reading and writing astronomical
files) or base classes for other
packages to utilize for a common interface (e.g., \texttt{NDData}).
In this section, we highlight new features introduced or substantially improved
since version v0.2 (previously described in \citealt{astropy}).

% \subsection{Analytic Functions}
% moved to models and depreciated --
% just here for completeness at the moment
\inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}
\inlinecomment{Tom R}{the only issue is if we rely on having e.g. units described first if they are used later}

@@

New model classes can be created in two ways:
\begin{enumerate}
   \item The simplest way is to use the \texttt{custom\_model} decorator in modeling with a user-defined function that takes the inputs and model parameters as arguments.
   \item It is also possible to subclass the \texttt{Model} base class and create an arbitrarily complex custom model.
\end{enumerate}

>>>>

%\subsection{Support of Astropy}
% Removing unless this gets written about in
% a later version
% This section should be a straight forward/factual description of the current
% funding and support provided to astropy with the purpose of explaining the
% current structure to the community

@@

\section{Astropy Core Package v2.0}
\label{sec:core}
% Adrian
The \astropy project aims to provide \python-based packages for all tasks that
are commonly needed in a large subset of the astronomical community.
At the foundation is the \astropypkg core package, which provides general
functionality (e.g., coordinate transformations, reading and writing astronomical
files) or base classes for other
packages to utilize for a common interface (e.g., \texttt{NDData}).
In this section, we highlight new features introduced or substantially improved
since version v0.2 (previously described in \citealt{astropy}).  The \astropkg 
provides a full log of changes \footnote{https://github.com/astropy/astropy/blob/master/CHANGES.rst} 
over the course of the entire project and more details about individual 
subpackages are available in the documentation \footnote{http://docs.astropy.org/en/stable/}.  
Beyond what is mentioned below, most subpackages have seen increased performance
since the release of the v0.2 package.

% \subsection{Analytic Functions}
% moved to models and depreciated --
% just here for completeness at the moment
%\inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}
%\inlinecomment{Tom R}{the only issue is if we rely on having e.g. units described first if they are used later}

@@

New model classes can be created in two ways:
\begin{enumerate}
   \item The simplest way is to use the \texttt{custom\_model} decorator in modeling with a user-defined function that takes the inputs and model parameters as arguments.
   \item It is also possible to create an arbitrarily complex custom model based on the \texttt{Model} class.
\end{enumerate}
